Think deep for reef resilience

### 2025-08-15 paper/paper_draft.qmd
Add source of carrying capacity estimates
Plus auto-format
Minor tweak

The spatial extent of the GBR reefs represented in this investigation follows the reef
definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA)
[@GBRMPA2022]. The reef definitions define 3806 reefs across the GBR. An indicative map of
the GBR marine park including the Marine Park management areas [@GBRMPA2007] and the
corresponding bioregion for each reef is shown in (@fig-region-map; [@GBRMPA2024]).

@@

ADRIA-CoralBlox was run for 4096 scenarios for each of the five GCMs (20,480 total model
runs). Here, a scenario represents a unique combination of assumed environmental (namely one
of the five DHW trajectories) and ecological factors including coral growth and mortality
rates, coral thermal tolerances. Scenarios were generated using the low-discrepancy Sobol'
sampling method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a random-Quasi
Monte Carlo approach which balances scenario exploration with improved convergence
properties (compared to pseudo-random sampling). A detailed comparative analysis of the
sampling methods can be found in [@kucherenko2015].

>>>>

The spatial extent of the GBR reefs represented in this investigation follows the reef
definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA)
[@GBRMPA2022]. The reef definitions define 3806 reefs across the GBR. An indicative map of
the GBR marine park including the Marine Park management areas [@GBRMPA2007] and the
corresponding bioregion for each reef is shown in (@fig-region-map; [@GBRMPA2024]).
Estimates of coral carrying capacity for each reef were taken from prior analyses undertaken
in [@bozec2022].

@@

ADRIA-CoralBlox was run for 4096 scenarios for each of the five GCMs (20,480 total model
runs). Here, a scenario represents a unique combination of assumed environmental (namely one
of the five DHW trajectories) and ecological factors including coral growth and mortality
rates, coral thermal tolerances. Scenarios were generated using the low-discrepancy Sobol'
sampling method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a random-Quasi
Monte Carlo approach which balances scenario exploration with improved convergence
properties compared to pseudo-random sampling. A detailed comparative analysis of the
sampling methods can be found in [@kucherenko2015].
